---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(ggplot2)
library(ggfun)
library(dplyr)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))

# Introdction

The package `ggfun` extends some of the existing `ggplot2` functionalities by wrapping up some new layer functions and existing methods. It totally including six packages,`stat_star`, `stat_rl`, `stat_ars`, `stat_arrowmap`, `geom_image`, and `layer_PersHomo`. It covers 3 aspects of the statistics field, statistical method, image visualization, mathematical algorithms. The object-oriented system we used is called `ggproto`, and the four aspects we extend are `stat`, `geom`, `theme`, and `faceting`.



## stat_star()

This function is a simple application of `ggplot2` extension functionlity in `stat` function. We provided an algorithm here to calculate the "distance" between points and the central point (defined by median) ginven a data set for scatter plot. And draw a line from the central point to the farthest point. It works with usual `line` geometry objects and applies our algorithm as `stat`.

The following two examples show the usage in a skewed distribution and a bell-shaped distribution.

```{r}
madedata1 <- data.frame(x = rnorm(n = 100, mean = 0, sd = 1), 
                        y = rf(n = 100, df1 = 5, df2 = 2))
madedata2 <- data.frame(x = rnorm(n = 100, mean = 0, sd = 1), 
                        y = rnorm(n = 100, mean = 0, sd = 1))

ggplot(madedata1, aes(x = x, y = y)) + 
  geom_point() + 
  stat_star()

ggplot(madedata2, aes(x = x, y = y)) + 
  geom_point() + 
  stat_star()
```

## stat_arrowmap()

This function follows the same logic from the above function. They both create new algorithms for certain purposes and make use of the existing geometry objects in `ggplot2`. This function is less general and focuses on a very specific goal that is to create a so called arrow map for the US elections. So it requires the US map information and a data set containing some elements needed to show here.

So usually before you can directly using this function, you need to organize your data into a required form. The required aesthetics are:

- `x`: usually longitude
- `y`: usually latitude
- `change`: the changes for each state (can be specified by group aesthetics, as one state by default).

Here we use a made up data set to illustrate the main usage of the function.

```{r fig.width=5}
usmap <- map_data("state")
madedata <- data.frame(region = unique(usmap$region), 
                                change = (runif(49)-0.5)*2,stringsAsFactors = FALSE)
madedata <- madedata %>%
  left_join(usmap,by = "region")

madedata %>%
  ggplot() +
  geom_path(aes(x = long, y = lat, group = group)) +
  stat_arrowmap(aes(x = long, y = lat, change = change, group = region))
```

This is not a good picture, however, notice that we can use the parameters in `geom_curve` here to modify the arrows to make them better since this function use the `curve` geometry object.

```{r fig.width=5}
madedata %>%
  ggplot() +
  geom_path(aes(x = long, y = lat, group = group)) +
  stat_arrowmap(aes(x = long, y = lat, change = change, group = region),
                curvature = 0.3, angle = 60,
                size = 1, arrow.fill = "yellow", 
                arrow = arrow(angle = 25,
                              type = "closed",
                              length = unit(0.1, "inches")))
```

## geom_image()

This function replaces the usual points object in `ggplot2` with provied image. This is different from the previous `stat` related functions, because it create a new geometry object instead of using the existing one. You can treat it like `geom_point` with the points replaced by your image.

Examples are shown below.

```{r , fig.width=5, fig.height=4}
path1 <- system.file("extdata", "donkey.jpg", package = "ggfun")
path2 <- system.file("extdata", "elephant.jpg", package = "ggfun")
p1 <- magick::image_read(path1)
p2 <- magick::image_read(path2)

mtcars %>%
  ggplot() + 
  geom_image(aes(x = wt, y = mpg), img = p1)

mtcars %>%
  ggplot() + 
  geom_image(aes(x = qsec, y = mpg), img = p2, size = 0.1)
```
