---
title: "ggfun"
author: "Yawei Ge, Zhenzhen Chen, Weiquan Luo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(ggplot2)
library(ggfun)
library(dplyr)
```



# Introdction

The package `ggfun` extends some of the existing `ggplot2` functionalities by wrapping up some new layer functions and existing methods. It totally including six packages,`stat_star`, `stat_rl`, `stat_ars`, `stat_arrowmap`, `geom_image`, and `layer_PersHomo`. It covers 3 aspects of the statistics field, statistical method, image visualization, mathematical algorithms. The object-oriented system we used is called `ggproto`, and the four aspects we extend are `stat`, `geom`, `theme`, and `faceting`.

`stat`: drawing the plot through some mathmatic algorithms. In `ggfun` package, `stat_ars`, `stat_star`,`stat_arrowmap`,  are using this function. 

`geom`:showing the geometry objects in the plot. In `ggfun` package, `geom_image` is using this function.

`faceting`:organizing different panels, and designing the layout. In this package, `layer_PersHomo` is using this function.




## stat_star

This function is a simple application of `ggplot2` extension functionlity in `stat` function. We provided an algorithm here to calculate the "distance" between points and the central point (defined by median) ginven a data set for scatter plot. And draw a line from the central point to the farthest point. It works with usual `line` geometry objects and applies our algorithm as `stat`.

### Example

The following two examples show the usage in a skewed distribution and a bell-shaped distribution.

```{r}
madedata1 <- data.frame(x = rnorm(n = 100, mean = 0, sd = 1), 
                        y = rf(n = 100, df1 = 5, df2 = 2))
madedata2 <- data.frame(x = rnorm(n = 100, mean = 0, sd = 1), 
                        y = rnorm(n = 100, mean = 0, sd = 1))

ggplot(madedata1, aes(x = x, y = y)) + 
  geom_point() + 
  stat_star()

ggplot(madedata2, aes(x = x, y = y)) + 
  geom_point() + 
  stat_star()
```


## stat_rl

This function is a application of `ggplot2` used to draw regression linear for each levels of the categorical variables. It does this by providing a new paramter called 'id', which can seperate the dataset by the levels of the categorical variable. 

The required aesthetics are:
  
- `x`: the numerical explanatory variable in the dataset 
- `y`: the numerical response variable in the dataset
- `id`: the categroical variable with more than two levels. 

### Example

'indexf' is dataset contain two numerical variable (length(cm) and width(cm)), and one categroical variable (sex (two levels: F, M)). 

```{r}
ggplot(indexf, aes(x = length, y = width, id = sex)) + 
  geom_point() + 
  stat_rl(aes(x = length, y = width, id = sex, col = sex))
```

We used `id` this parameter to separate the dataset based on the levels of the categorical variable. For the plot, we can clearly to see that there are two regression lines for each level. The basic code and rule, we need for this function just following the `ggplot2` package.


## stat_ars

This function applied the mathematical algorithm to calculate the Archimedean Spiral. We built this function that can automatically to calculate the Archimedean Spiral and draw the spiral. It used the `line` geometry objects and applies the algorithm as `stat`. 

The required parameters are:

- `a`: rotating the spiral
- `b`: the distance control between two adjacent curves
- `n`: the number of turns

### Example

```{r}
ggplot() + 
  stat_ars(aes(a = 8, b = 2, n = 2), col = "lightblue")
```

From this plot, we can see that once the users input the three basic parameters for Archimedean Spiral, the function will automatically draw a spiral. We can also be based on adjusting these three parameters to see how each index will affect the spiral. For example, once you increase the `b`, the spiral will increase the distance between two curves.


## geom_image

This function replaces the usual points object in `ggplot2` with provied image. This is different from the previous `stat` related functions, because it create a new geometry object instead of using the existing one. You can treat it like `geom_point` with the points replaced by your image.

### Example

```{r , fig.width=5, fig.height=4}
path1 <- system.file("extdata", "donkey.jpg", package = "ggfun")
path2 <- system.file("extdata", "elephant.jpg", package = "ggfun")
p1 <- magick::image_read(path1)
p2 <- magick::image_read(path2)

mtcars %>%
  ggplot() + 
  geom_image(aes(x = wt, y = mpg), img = p1)

mtcars %>%
  ggplot() + 
  geom_image(aes(x = qsec, y = mpg), img = p2, size = 0.1)
```


## stat_arrowmap

This function follows the same logic from the above function. They both create new algorithms for certain purposes and make use of the existing geometry objects in `ggplot2`. This function is less general and focuses on a very specific goal that is to create a so called arrow map for the US elections. So it requires the US map information and a data set containing some elements needed to show here.

So usually before you can directly using this function, you need to organize your data into a required form. The required aesthetics are:

- `x`: usually longitude
- `y`: usually latitude
- `change`: the changes for each state (can be specified by group aesthetics, as one state by default).

### Example

Here we use a made up data set to illustrate the main usage of the function.

```{r fig.width=5}
usmap <- map_data("state")
madedata <- data.frame(region = unique(usmap$region), 
                                change = (runif(49)-0.5)*2,stringsAsFactors = FALSE)
madedata <- madedata %>%
  left_join(usmap,by = "region")

madedata %>%
  ggplot() +
  geom_path(aes(x = long, y = lat, group = group)) +
  stat_arrowmap(aes(x = long, y = lat, change = change, group = region))
```

This is not a good picture, however, notice that we can use the parameters in `geom_curve` here to modify the arrows to make them better since this function use the `curve` geometry object.

```{r fig.width=5}
madedata %>%
  ggplot() +
  geom_path(aes(x = long, y = lat, group = group)) +
  stat_arrowmap(aes(x = long, y = lat, change = change, group = region),
                curvature = 0.3, angle = 60,
                size = 1, arrow.fill = "yellow", 
                arrow = arrow(angle = 25,
                              type = "closed",
                              length = unit(0.1, "inches")))
```


## layer_PersHomo

Given a points set as Geographic locations in a data.frame, extends `ggplot2` functionality to draw a line from location to location with defined criterion of distance in km. The concept is inhered from persist homology. The linkage in resulting figures can be used to recognize patterns or cluster of points. Compare to `ggplot2` package, plotly package might be better for this functionality because the linkage can be shown on the globe instead of a flat figure. To the purpose of the package, this layer attempt to show the capability of `ggplot2` on a small scale data instead of global data.

The required input are:

- `data`: a dataframe that each row contain longitude, latitude. 
- `x`: longitude in the input dataframe.
- `y`: latitude in the input dataframe.
- `d`: the magnitude of real Geo distance (in km) used as the criterion to link two locations.

### Example

The following example show the earthquake data with in Pacific Plate.

```{r}
library(magrittr)
library(ggplot2)
library(dplyr)
## plot base map
worldmap <- map_data("world2")
p <- ggplot() +
  geom_polygon(data=worldmap,
  aes(x=long, y=lat, group = group),
  fill="white", colour="#7f7f7f", size=0.5) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        plot.background=element_blank());
data(eqRaw)
eq <- eqRaw %>%
  filter(LONGITUDE > 110 | LONGITUDE < -45) %>%
  mutate(LONGITUDE = ifelse(LONGITUDE < 0, LONGITUDE + 360, LONGITUDE))
## add layer_PersHomo
fp <- p + layer_PersHomo(data= eq,mapping = aes(x=LONGITUDE, y=LATITUDE),
  d=450000, colour = "blue") + geom_point(); fp
```

The world map shows the so-called Ring of fire for the geographical area, where contains 90 percent of the historical earthquake and 81 percent of the greatest earthquake in the world. The red point is the estimated geographical location of the historical earthquake events. By defining the `d` parameter in km at the `layer_PersHomo` layer function, the blue lines are added to the map by connecting any two locations that their distance is less than the defined. All the blue lines as a whole show number of clusters of the points. The clusters are the active earthquake zone as well as the transform faults along the boundaries between the Pacific plate and other plates. Different values in `d` parameter result different in cluster size because of the merge or splits of the cluster. By changing the `d` parameter, we can understand the geographic major and minor faults.
